An Analysis of Security Vulnerabilities in Container Images for Scientific Data Analysis

### 2020-10-23 paper.tex
added descrepancies paragraph

\begin{figure*}
\includegraphics[width=\textwidth]{Figures/results.pdf}
\caption{\label{fig:vulnerabilities} Number of vulnerabilities detected by
Anchore in container images. \textbf{(A)} Number of vulnerabilities by
container image and severity, showing hundreds of detected vulnerabilities
per image (mean: 468). \textbf{(B)} Effect of image minification and
package update on 5 container images, showing that both techniques are
complementary \textbf{(C)} Number of vulnerabilities by number of
packages, showing a strong linear relationship. \textbf{(D)} Number of
vulnerabilities by number of packages \emph{after package update}, showing that software updates 
importantly reduce the number of detected vulnerabilities.}
\end{figure*}

@@

% where do the discrepancies come from?
The vulnerabilities detected by Anchore only (region \textbf{(1)} in
Fig~\ref{fig:venn}) are all in the development package (headers) of the C
library (\texttt{linux-libc-dev} in Ubuntu). \tristan{not all in fact... I
wasn't sure how to interpret all these differences (see last section in the
notebook), let's discuss it during a meeting.}

% \begin{table*}
% 	\csvreader[%
% 	 tabular={|c|c|c|c|c|c|},
% 		table head = \hline\textbf{Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
% 		late after line= \\,
% 			late after last line=\\\hline %
% 		]{resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
% 			{\labels & \names & \A & \C & \V & \Stools}
% 		   \centering
% 		\vspace*{1mm}
% 		\caption{\label{table1}Number of vulnerabilities detected by the four scanners. Vuls shows \textit{no data} for images \texttt{bids/antscorticalthickness:v2.2.0-1} and \texttt{bids/afni\_proc:latest}
% 		since their OS distributions reached end of life.} 
% 	\end{table*}
	\begin{figure}
        \includegraphics[width=\columnwidth]{Figures/venn.pdf}
	\caption{\label{fig:venn} Differences between the vulnerabilities detected
	by the different scanners. The Jaccard coefficients between the sets of
	detected vulnerabilities are quite low, showing important discrepancies
	between the scanners: Jaccard(Anchore, Clair) = 0.59, Jaccard(Anchore, Vuls) =
	0.59, Jaccard(Vuls, Clair) = 0.82. Two Ubuntu 17.04 images weren't
	included in this comparison as they cannot be scanned by Vuls.
	\tristan{add Centos images to the analysis using the notebook}}
\end{figure}

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{Figures/results.pdf}
\caption{\label{fig:vulnerabilities} Number of vulnerabilities detected by
Anchore and Stools in container images. \textbf{(A)} Number of vulnerabilities by
container image and severity, showing hundreds of detected vulnerabilities
per image. Images s*,t*,u*,v*,w* and x* are Singularity images and scanned by Stools. \textbf{(B)} Effect of image minification and
package update on 5 container images, showing that both techniques are
complementary \textbf{(C)} Number of vulnerabilities by number of
packages, showing a strong linear relationship. \textbf{(D)} Number of
vulnerabilities by number of packages \emph{after package update}, showing that software updates 
importantly reduce the number of detected vulnerabilities.}
\end{figure*}

@@

% where do the discrepancies come from?
We analyzed these results and figured out some reasons behind the discrepancies of the results.
The 4443 out of 4453 vulnerabilities detected by Anchore only (region \textbf{(1)} in
Fig~\ref{fig:venn}) are in the development package (headers) of the C
library (\texttt{linux-libc-dev} in Ubuntu and Debian). Clair detects only Debian vulnerabilities
in \texttt{linux-libc-dev}, whereas Vuls do not detect vulnerabilities in this package at all.
The remaining 10 vulnerabilities in region \textbf{1} are reported in the binary or subpackages 
of vulnerable packages, which is not reported by Vuls and Clair.
Also, Anchore filters the vulnerabilities that are \texttt{minor} and 
ignored by Debian. These are the main reasons behind vulnerabilities in 
region \textbf{2} and region \textbf{3}. Clair's wrong detections also adds up to region \textbf{3}.
Vulnerabilities in region \textbf{4} all exist in Ubuntu distribution 
and are not detected by Clair. We noticed that this is happening because Clair refers 
to Ubuntu CVE tracker database and in this database there are two entries for Ubuntu 14.04, 
one for LTS and another for ESM release. Clair mistakenly grabs ESM entry and detects vulnerabilities 
according to it, whereas LTS release is present in the image. There are also a couple of 
bugs in Anchore which we noticed in our analysis and reported to the Anchore's developer 
team through their Slack channel. First is the \textit{epoch bug}, which gets triggered 
when there is an epoch (\texttt{:}) in the package version. Another is \textit{out of standard bug}, 
which gets triggered when the vulnerability is ignored 
by Ubuntu. These two bugs are also the reasons behind vulnerabilities in region \textbf{6} 
in addition to Anchore intentionally ignoring \texttt{minor} Debian vulnerabilities. 
Furthermore, Vuls reports vulnerabilities which have \textit{TEMP} 
identifier, whereas both Clair and Anchore decides not to report them. These 
vulnerabilities have a temporary identifier and can be changed anytime so it is not
recommended for external references. There are 32 temporary vulnerabilities in region \textbf{7}.
The remaining vulnerabilities in this region exist in Centos distribution and according to our analysis
these are the misses in Anchore and Clair.

% \begin{table*}
% 	\csvreader[%
% 	 tabular={|c|c|c|c|c|c|},
% 		table head = \hline\textbf{Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
% 		late after line= \\,
% 			late after last line=\\\hline %
% 		]{resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
% 			{\labels & \names & \A & \C & \V & \Stools}
% 		   \centering
% 		\vspace*{1mm}
% 		\caption{\label{table1}Number of vulnerabilities detected by the four scanners. Vuls shows \textit{no data} for images \texttt{bids/antscorticalthickness:v2.2.0-1} and \texttt{bids/afni\_proc:latest}
% 		since their OS distributions reached end of life.} 
% 	\end{table*}
	\begin{figure}
        \includegraphics[width=\columnwidth]{Figures/venn.pdf}
	\caption{\label{fig:venn} Differences between the vulnerabilities detected
	by the different scanners. The Jaccard coefficients between the sets of
	detected vulnerabilities are quite low, showing important discrepancies
	between the scanners: Jaccard(Anchore, Clair) = 0.59, Jaccard(Anchore, Vuls) =
	0.59, Jaccard(Vuls, Clair) = 0.82. Two Ubuntu 17.04 images weren't
	included in this comparison as they cannot be scanned by Vuls.}
\end{figure}
